B\'{e}zier $\bar{B}$ projection

### 2018-01-09 projection1120.tex
update

Following the same pattern of non-symmetric \Bezier $\bar{B}$ in Timoshenko beam problem, we keep the discretization of $\mathbf{u}$ and $\mathbf{w}$ untouched, while use lower order spline basis functions and corresponding dual basis functions for the discretization of pressure $p$ and its variation $\delta{p}$, respectively. The discretized stiffness matrix in mixed form can be written as
\begin{equation}
    \mathbf{K}_{mix}=
    \begin{bmatrix}
        \mathbf{K}^{dev} & -\mathbf{P}^{T}\\
        -\hat{\mathbf{P}} & -\dfrac{1}{(\lambda+2\mu/3)}\mathbf{I}
    \end{bmatrix},
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e^{vol},
\end{equation}
with
\begin{equation}
    \mathbf{P}_e^{vol}=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^{vol}_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
By eliminating the pressure control points, we obtain the pure displacement formulation as
\begin{equation}
	\mathbf{K} = \mathbf{K}^{dev} + \bar{\mathbf{K}}^{vol}_{NS},
\end{equation}
where
\begin{equation}
    \bar{\mathbf{K}}^{vol}_{NS}=(\lambda+2\mu/3)\hat{\mathbf{P}}^T{\mathbf{P}}.
\end{equation}

@@

\subsubsection{Numerical evaluation of the inf-sup condition}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=.8\linewidth]{Cook_s_membrane}
   	\includegraphics[width=.8\linewidth]{Cook_s_membrane_zoomin}
	\caption{Cook's membrane: comparison of the vertical displacement at the top right corner for the different methods and degrees.}
	\label{fig:Cook's_result}
\end{figure}

@@

\added{The contour plots of $\sigma_{xx}$ for bicubic elements of the third mesh are shown in Figure \ref{fig:platewithhole_contour}, $Q_3$ elements are severely locked while all $\bar{B}$ methods converge to the reference solution. }
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.31\linewidth]{deformation_p_2} & \includegraphics[width=.31\linewidth]{deformation_p_3} & \includegraphics[width=.31\linewidth]{deformation_p_4}\\
\includegraphics[width=.31\linewidth]{stress_p_2} & \includegraphics[width=.31\linewidth]{stress_p_3} & \includegraphics[width=.31\linewidth]{stress_p_4}\\
\includegraphics[width=.31\linewidth]{energy_p_2} & \includegraphics[width=.31\linewidth]{energy_p_3} & \includegraphics[width=.31\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}

\begin{figure}[htb!]
    \center
    \begin{tabular}{cc}
    \includegraphics[width=.4\linewidth]{no_stress_contour} & \includegraphics[width=.4\linewidth]{g_stress_contour}\\
    $Q_3$ & $\mathcal{T}^{L^2} Q_3/Q_2$\\
    \includegraphics[width=.4\linewidth]{s_stress_contour} & \includegraphics[width=.4\linewidth]{ns_stress_contour}\\
    $S-\mathcal{T}^{p} Q_3/Q_2$ & $NS-\mathcal{T}^{p} Q_3/Q_2$\\
    \includegraphics[width=.4\linewidth]{reference_stress_contour} & \includegraphics[width=.13\linewidth]{legend}\\
    Exact & Legend
    \end{tabular}
        \caption{Contour plots of $\sigma_{xx}$ for the plate with a circular hole ($p=3$, the $3^{rd}$ mesh is used).}
        \label{fig:platewithhole_contour}
    \end{figure}
\section{Conclusions}
\label{sec:conclusion}

>>>>

\subsubsection{\added{Discretization}}

Following the same pattern of non-symmetric \Bezier $\bar{B}$ in Timoshenko beam problem, we keep the discretization of $\mathbf{u}$ and $\mathbf{w}$ untouched, while use lower order spline basis functions and corresponding dual basis functions for the discretization of pressure $p$ and its variation $\delta{p}$, respectively. The discretized stiffness matrix in mixed form can be written as
\begin{equation}
    \mathbf{K}_{mix}=
    \begin{bmatrix}
        \mathbf{K}^{dev} & -\mathbf{P}^{T}\\
        -\hat{\mathbf{P}} & -\dfrac{1}{(\lambda+2\mu/3)}\mathbf{I}
    \end{bmatrix},
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e^{vol},
\end{equation}
with
\begin{equation}
    \mathbf{P}_e^{vol}=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^{vol}_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
By eliminating the pressure control points, we obtain the pure displacement formulation as
\begin{equation}
	\mathbf{K} = \mathbf{K}^{dev} + \bar{\mathbf{K}}^{vol}_{NS},
\end{equation}
where
\begin{equation}
    \bar{\mathbf{K}}^{vol}_{NS}=(\lambda+2\mu/3){\mathbf{P}}^T\hat{\mathbf{P}}.
\end{equation}

@@

\subsubsection{\added{Numerical evaluation of the inf-sup condition}}

@@

\begin{figure}[htb!]
    \centering
	\begin{subfigure}[b]{\textwidth}
        \includegraphics[width=.8\linewidth]{Cook's_membrane_Q1}
    \end{subfigure}
    %
    \centering
	\begin{subfigure}[b]{\textwidth}
        \includegraphics[width=.8\linewidth]{Cook's_membrane_Q2}
    \end{subfigure}
\end{figure}

\begin{figure}[htb!]\ContinuedFloat
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=.8\linewidth]{Cook's_membrane_Q3}
    \end{subfigure}
    %
    \centering
     \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=.8\linewidth]{Cook's_membrane_Q4}
    \end{subfigure}
	\caption{Cook's membrane: comparison of the vertical displacement at the top right corner for the different methods and degrees.}
	\label{fig:Cook's_result}
\end{figure}

@@

\added{The error contour plots of $\sigma_{xx}$ for biquartic elements of the fifth mesh are shown in Figure \ref{fig:platewithhole_contour}, $Q_4$ elements are severely locked while all $\bar{B}$ methods converge to the reference solution. }
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.31\linewidth]{deformation_p_2} & \includegraphics[width=.31\linewidth]{deformation_p_3} & \includegraphics[width=.31\linewidth]{deformation_p_4}\\
\includegraphics[width=.31\linewidth]{stress_p_2} & \includegraphics[width=.31\linewidth]{stress_p_3} & \includegraphics[width=.31\linewidth]{stress_p_4}\\
\includegraphics[width=.31\linewidth]{energy_p_2} & \includegraphics[width=.31\linewidth]{energy_p_3} & \includegraphics[width=.31\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}

\begin{figure}[htb!]
    \center
    \begin{tabular}{cc}
    \includegraphics[width=.4\linewidth]{no} & \includegraphics[width=.4\linewidth]{g}\\
    $Q_4$ & $\mathcal{T}^{L^2} Q_4/Q_3$\\
    \includegraphics[width=.4\linewidth]{s} & \includegraphics[width=.4\linewidth]{ns}\\
    $S-\mathcal{T}^{p} Q_4/Q_3$ & $NS-\mathcal{T}^{p} Q_4/Q_3$
    \end{tabular}
        \caption{Contour plots of $\vert{\sigma_{xx}-\sigma_{xx}^h}\vert$ for the plate with a circular hole ($p=4$, the $5^{th}$ mesh is used).}
        \label{fig:platewithhole_contour}
    \end{figure}
\section{Conclusions}
\label{sec:conclusion}
